---
title: "Plot_ly"
author: "Ditian Li"
date: "2018/11/1"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---
Chart A, the trend of orders is roughly same across week(fresh fruits, fresh vegetables, packaged fruits and vegetables changed across week ).
Chart B, the top2 popular aisles are fresh vegetables and fresh fruits.
Chart C, compare the trend of orders of fresh vegatables and fresh fruits, they are at similar trend, from 12-14 o'clock there are less fresh fruits orders than fresh vegetables.

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(tidyverse)
library(viridis)
library(p8105.datasets)
library(plotly)
devtools::install_github("p8105/p8105.datasets")
library(p8105.datasets)
```

Column {data-width=500}
-----------------------------------------------------------------------

### Chart A: 3D plot to show the trend of orders of different aisles across week.

```{r}

 instacart1 <- instacart %>% 
  group_by(aisle,order_dow) %>% 
  summarize(n_item = n()) 
  
  instacart1%>% 
  plot_ly(x = ~order_dow, y =  ~aisle, z = ~n_item,
          color = ~order_dow)

```

Column {data-width=500}
-----------------------------------------------------------------------

### Chart B: Bar chart to show order amounts for different aisles.

```{r}
instacart %>% 
  group_by(aisle) %>% 
  summarize(n_item = n()) %>% 
  arrange(desc(n_item)) %>% 
   mutate(aisle = fct_reorder(aisle, n_item)) %>% 
  plot_ly(x = ~aisle, y = ~n_item, color = ~aisle, type = "bar")
```

### Chart C: Line plot to compare trends across day for the two most popular aisles.

```{r}
fresh_vegetables <- instacart %>% 
  group_by(aisle,order_hour_of_day) %>% 
  filter(aisle == "fresh vegetables") %>% 
  summarize(n_item = n()) %>% 
  mutate(n_item1 = n_item)

fresh_fruits <- instacart %>% 
  group_by(aisle,order_hour_of_day) %>% 
  filter(aisle == "fresh fruits") %>% 
  summarize(n_item = n()) %>% 
 mutate(n_item2 = n_item)

data<- data.frame(fresh_vegetables,fresh_fruits)


plot_ly(data, x = ~order_hour_of_day, y = ~n_item1, name = 'fresh vegetables', type = 'scatter', mode = 'lines') %>%
  add_trace(y = ~n_item2, name = 'fresh fruits', mode = 'lines') 
```